R Markdown Features

### 2018-10-23 GitHubPage/my_R_book/Rmarkdown_features/00-yaml.rmd
up

You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
```{yaml}
---
author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
output:
  pdf_document:
    latex_engine: xelatex    
    includes:
        in_header: header.tex
documentclass: article
urlcolor: "blue"
linestretch: 1.5
fontsize: 12pt 
geometry: a5paper, headheight=0pt, margin=0.4in
---
```

@@

## PDF 2 {-}
This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
```{yaml}
---
author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
output:
  bookdown::pdf_document2:
    number_sections: FALSE
    toc: False
    includes:
      in_header: header.tex
    latex_engine: xelatex
  bookdown::html_document2:
    number_sections: FALSE
    includes:
      before_body: mathjax_bm.tex
urlcolor: blue
always_allow_html: yes
linestretch: 1.5
---
```

>>>>

You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
```{yaml}
---
author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
output:
  pdf_document:
    latex_engine: xelatex    
    includes:
        in_header: header.tex
documentclass: article
urlcolor: "blue"
linestretch: 1.5
fontsize: 12pt 
geometry: a5paper, headheight=0pt, margin=0.4in
linestretch: 1.5
links-as-notes: true
---
```

@@

## PDF 2 {-}
This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
```{yaml}
---
author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
output:
  bookdown::pdf_document2:
    number_sections: FALSE
    toc: False
    includes:
      in_header: header.tex
    latex_engine: xelatex
  bookdown::html_document2:
    number_sections: FALSE
    includes:
      before_body: mathjax_bm.tex
urlcolor: blue
always_allow_html: yes
linestretch: 1.5
geometry: a4paper #, headheight=0pt, margin=0.4in, landscape
links-as-notes: true
---
```

### 2018-10-23 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

---
title: "R Markdown Features"
subtitle: "A Compact Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa.csl
link-citations: yes
output:
  bookdown::html_document2:
    css: style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

# (PART) yaml {-}
```{r child='00-yaml.rmd'}
```

# (PART) knitr {-}
```{r child='01-knitr.rmd'}
```

# (PART) LaTeX {-}
```{r child='02-latex.rmd'}
```

# (PART) Presentation {-}
```{r child='03-slide.rmd'}
```

>>>>

---
title: "R Markdown Features"
subtitle: "A Compact Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa.csl
link-citations: yes
output:
  bookdown::html_document2:
    css: style.css
    df_print: kable
    toc: true
    toc_depth: 1
    toc_float:
        collapsed: false
---

@@

# (PART) **yaml** {-}
<br>

```{r child='00-yaml.rmd'}
```

# (PART) **knitr** {-}
<br>

```{r child='01-knitr.rmd'}
```

# (PART) **LaTeX** {-}
<br>

```{r child='02-latex.rmd'}
```

# (PART) **Presentation** {-}
<br>

```{r child='03-slide.rmd'}
```
